A Fredholm operator approach to the plate buckling problem

### 2018-06-23 doc/draft-01/01intro.tex
update paper, build out introduction

\begin{align}
\Delta (\Delta + k^2) w &= 0 \quad \text{in} \quad \Omega \label{eq:buck1} \; , \\
w &= 0 \quad \text{on} \quad \Gamma \label{eq:buck2} \; ,\\
\dwdn &=0 \quad \text{on} \quad \Gamma \label{eq:buck3} 
\end{align}
has a non-trivial solution. In a slight abuse of notation,
these values and the corresponding solutions are often
referred to as ``eigenvalues'' and ``eigenfunctions'',
respectively. 
It is well known that the buckling problem has a
countable collection of such values
$0 < k_{1}^{2} \leq k_{2}^2 \leq \ldots \uparrow \infty$,
counting multiplicites.

The eigenvalues (and eigenfunctions)
of the boundary value problem \cref{eq:buck1,eq:buck2,eq:buck3}
describe the critical buckling load (and deflection)
of a thin plate under
a compressive force applied along the edge. While the
isotropy and homogeneity assumptions are restrictive,
the equations are still of interest in materials design
(CITATIONS). The analytical properties of the eigenvalues and
eigenfunctions are also of interest from a mathematical
perspective, often as they contrast with the eigenvalues
and eigenmodes of an idealized drum (CITATIONS).

Numerical simulations have long played an important
in the analyses described above and there are a number
of available methods (note that some of the references
included here are written in terms of the related
Stokes eigenvalue problem, which has equivalent
eigenvalues on simply connected domains).
The differential equation can
be discretized directly, resulting in a discrete
generalized eigenvalue problem for the buckling
eigenvalues \cite{jia2009approximation}. Integral
equation methods \cite{kitahara2014boundary} are
a natural choice for this problem, because (a) the
fourth order term induces strong
ill-conditioning when the differential equation
is discretized directly and (b) the problem is reduced
to one defined on the domain alone, requiring fewer
degrees of freedom to resolve the solution.

>>>>

\begin{align}
\Delta (\Delta + k^2) w &= 0 \quad \textrm{in} \quad \Omega \label{eq:buck1} \; , \\
w &= 0 \quad \textrm{on} \quad \Gamma \label{eq:buck2} \; ,\\
\dwdn &=0 \quad \textrm{on} \quad \Gamma \label{eq:buck3} 
\end{align}
has a non-trivial solution. In a slight abuse of notation,
these values and the corresponding solutions are often
referred to as ``eigenvalues'' and ``eigenfunctions'',
respectively. 
It is well known that the buckling problem has a
countable collection of such values
$0 < k_{1}^{2} \leq k_{2}^2 \leq \ldots \uparrow \infty$,
counting multiplicites.

The eigenvalues (and eigenfunctions)
of the boundary value problem \cref{eq:buck1,eq:buck2,eq:buck3}
describe the critical buckling load (and deflection)
of a thin plate under
a compressive force applied along the edge. While the
isotropy and homogeneity assumptions are restrictive,
the equations are still of interest in materials design
(CITATIONS). The analytical properties of the eigenvalues and
eigenfunctions are also of interest from a mathematical
perspective, often as they contrast with the eigenvalues
and eigenmodes of an idealized drum (CITATIONS). For instance,
it is well-known that the first eigenfunction of the
drum problem (i.e. the eigenvalue problem of the Laplace
equation with homogeneous Dirichlet boundary conditions)
is either nonpositive or nonnegative on any domain.
In contrast, it is possible for the first buckling
eigenfunction of a convex domain with analytic boundary
to take both positive and negative values \cite{antunes2011buckling}.

Numerical simulations have long played an important
in the analyses described above and there are a number
of available methods (note that some of the references
included here are written in terms of the related
Stokes eigenvalue problem, which has equivalent
eigenvalues on simply connected domains). We do not
seek to review the literature here but will provide
some context for the present work. Finite element methods
are ubiquitous in mechanical engineering applications
and are flexible both with respect to the governing
equations and the shape of the domain. Such a method
would first obtain a ``weak'' form of the equations
\cref{eq:buck1,eq:buck2,eq:buck3} and then 
approximate the solution space in some
finite dimensional basis, resulting in a discrete model
for the buckling problem.
The eigenvalues $k^2$ are then
approximated by the eigenvalues of the discrete
model \cite{johnson1974beam,rannacher1979nonconforming,
  jia2009approximation,carstensen2014guaranteed}.
Because of the fourth order term in \cref{eq:buck1},
the system matrices resulting from a finite element
discretization can have large condition numbers (growing
like $h^4$ where $h$ is the diameter of a typical element
in the discretization) which can cause numerical instability.

Integral equation methods \cite{kress1989linear,
  atkinson2009numerical,kitahara2014boundary} present
a natural alternative to the finite element method
for the buckling problem, because (a) the
integral representation acts as an analytical preconditioner
for the fourth order term and (b) the problem is reduced
to one defined on the boundary of the domain alone,
requiring fewer degrees of freedom to resolve the solution
on a complex domain. In an integral equation method,
the solution $w$ is represented in terms of a sum of
two layer potentials (which a priori satisfy
\cref{eq:buck1}) with unknown densities. Substituting this
representation into the boundary conditions
\cref{eq:buck2,buck3} results in an integral equation
for the unknown densities, which
is in turn discretized using numerical quadrature.
Unlike the original equation \cref{eq:buck1} and the weak
formulation used in a finite element method, the integral
equation for the unknown densities has a nonlinear dependence
on the parameter $k^2$. In an integral equation method, then,
the eigenvalues are found by searching for the values
of $k^2$ where the discrete system for the unknown densities
is no longer invertible.

While integral equation methods for the buckling problem
have been considered previously, the existing formulations
have resulted in first kind integral equations, i.e. equations
in which the operator is compact \cite{kitahara2014boundary,
  antunes2011buckling}. This is unsatisfying from a theoretical
perspective, because such operators are never invertible
(though, they are injective precisely when $k^2$ is an
eigenvalue \cite{kitahara2014boundary}) so that the
relation between the non-invertibility of the discrete system
and the eigenvalues is obscured. Further, such representations
create numerical challenges because common measures of the
``non-invertibility'' of a matrix, like the smallest singular
value or the determinant, converge to zero for all values of
$k^2$ as the boundary is refined.

Second kind integral equations, i.e. equations in which the
operator is Fredholm ...

### 2018-06-23 doc/draft-01/02prelim.tex
update paper, build out introduction

\subsection{Fundamental solution}

The fundamental solution of the Helmholtz-Biharmonic equation is
given by 
\begin{equation}
  G_{BH}(\xx,\yy) = -\frac{1}{k^2}
  \left (\frac{1}{2\pi} \log |\xx-\yy| +
  \frac{i}{4} H_0^{(1)}(k|\xx-\yy|) \right ) \, , 
\end{equation}
where $k$ is the Helmholtz paramater in the Helmholtz-Biharmonic equation,
and $H_{0}^{1}(r)$ is the Hankel function of the first kind of order zero.

@@

In \cite{Farkas89}, Farkas derived integral equation formulations
for the solution of the Dirichlet problem for the biharmonic equation ($k=0$). 
In this formulation, the solution 
$w$ is represented as a sum of two layer potentials
\begin{equation}
  w(\xx) = \int_\Gamma K_1^F (\xx,\yy) \sigma_1(\yy) \, dS(\yy)
  + \int_\Gamma K_2^F(\xx,\yy) \sigma_2(\yy) \, dS(\yy) \; ,
  \label{eq:farkRep}
\end{equation}
where $\sigma_{1}$, and $\sigma_{2}$ are unknown densities, and the kernels
$K_{1}^{F}$, and $K_{2}^{F}$ are linear combinations of derivatives of
the biharmonic Green's function and appropriately chosen to get second kind integral equations
for the unknown densities $\sigma_{1}$ and $\sigma_{2}$ on imposing the boundary conditions.

In \cite{shidongmodbi}, Jiang extended the Farkas formulation for the solution of the modified
biharmonic equation, albeit for different boundary conditions. With minor modifications, their formulation
can also be adopted for the solution of the Dirichlet problem for the Helmholtz-biharmonic equation
\begin{align}
\Delta (\Delta + k^2) w &= 0 \quad \text{in} \quad \Omega \label{eq:helmbi} \\
w &= f \quad \text{on} \quad \Gamma \\
\dwdn &=g \quad \text{on} \quad \Gamma \,,
\end{align}
where $f,g$ are prescribed functions on the boundary.

For two points on the plane, $\xx$ and $\yy$, let $\br = \yy - \xx$. Let the kernels $K_{1}^{F}$, and 
$K_{2}^{F}$ be defined by 
\begin{align}
  K_1^F(\xx,\yy) &= \partial_{n_{y}n_{y}n_{y}}\Gbh(\xx,\yy)
  + 3 \partial_{n_{y}\tau_{y}\tau_{y}}\Gbh(\xx,\yy) + k^{2} \partial_{n_{y}}\Gbh(\xx,\yy)\; , \label{eq:kf1} \\
  K_2^F(\xx,\yy) &= -\partial_{n_{y}n_{y}}\Gbh(\xx,\yy)
  + \partial_{\tau_{y}\tau_{y}}\Gbh(\xx,\yy) \label{eq:kf2} \; .
\end{align}
More explicitly, we have
\begin{align}
  K_1^F(\xx,\yy) &=  -\dfrac{\br \cdot \bn(\yy)}{|\br|^2}  \cdot \left( \frac{3 i}{2} H_0^{(1)}(k|\br|) - \frac{5 i}{2 k|\br|} H_1^{(1)}(k|\br|) + \frac{6}{\pi k^2 |\br|^2} + \frac{1}{2\pi}  \right) +     \\
  & \quad \dfrac{\left(\br \cdot \bn(\yy)\right)^3}{|\br|^4} \cdot \left( 2i H_0^{(1)}(k|\br|) - \frac{7 i}{2 k|\br|} H_1^{(1)}(k|\br|) + \frac{8}{\pi k^2 |\br|^2}  \right) \, , \nonumber \\
  K_2^F(\xx,\yy) &=  -\left(\frac{1}{2}-\dfrac{\left(\br \cdot \bn(\yy)\right)^2}{|\br|^2} \right)  \cdot \left( \frac{i}{2} H_0^{(1)}(k|\br|) - \frac{i}{k|\br|} H_1^{(1)}(k|\br|) + \frac{2}{\pi k^2 |\br|^2}  \right)\; .
\end{align}

On enforcing the Dirichlet boundary conditions for
$w$, we obtain the integral equation
\begin{equation}
  \begin{split}
    \begin{pmatrix}
      f(\xx) \\
      g(\xx)
    \end{pmatrix} &= 
    \int_\Gamma
    \begin{pmatrix}
      K_{11}^F(\xx,\yy) & K_{12}^F(\xx,\yy) \\
      K_{21}^F(\xx,\yy) & K_{22}^F(\xx,\yy)
    \end{pmatrix}
    \begin{pmatrix}
      \sigma_1(\yy)\\
      \sigma_2(\yy)
    \end{pmatrix}
    \, dS(\yy) \\
    &\quad + \begin{pmatrix}
      1/2 & 0 \\
      -\kappa(\xx) & 1/2
    \end{pmatrix}
    \begin{pmatrix}
      \sigma_1(\xx)\\
      \sigma_2(\xx)
    \end{pmatrix} \; , \label{eq:farkIntEq} 
  \end{split}
\end{equation}
where $\kappa$ is the signed curvature at $\xx \in \Gamma$.
The kernels are given
by $K_{11}^F = K_1^F$, $K_{12}^F = K_2^F$,
\begin{align}
  K_{21}^F(\xx,\yy) &= \left(K_1^F(\xx,\yy)\right )_{n_x} \nonumber \\
  &= \bn(\xx) \cdot \nabla_{\xx} K_{21}^{F}(\xx,\yy) \; \label{eq:farkK21},\\
  K_{22}^F(\xx,\yy) &= \left(K_2^F(\xx,\yy)\right )_{n_x} \nonumber \\
  &= \bn(\xx) \cdot \nabla_{\xx} K_{22}^{F}(\xx,\yy) \label{eq:farkK22} \; .
\end{align}

@@

\begin{proof}
The proof is a minor modification of the one presented in~\ref{eq:shidongmodbi} and is contained in~\cref{sec:app}.
\end{proof}

The kernels $K^F_1$ and $K^F_2$ are
constructed with the goal that the $K^F_{ij}$ are
as smooth as possible. Suppose that the boundary
$\Gamma$ is of class $C^k$. Then, the kernels,
$K^F_{ij}(\xx,\yy)$, are $C^{k-2}$ functions on the boundary
for each $\yy \in \Gamma$.
Therefore, on a smooth
boundary, these kernels are smooth. However, on a
domain with a corner, we note 
that the kernel $K_{21}^F$
has a singularity with strength $r^{-2}$ (see~\cref{fig:ker21plot}). 
This singularity, in addition to the term in \cref{eq:farkIntEq}
which explicitly involves the
curvature, makes the representation \cref{eq:farkRep}
unstable for domains with high curvature (or
corners).

\subsection{Helmholtz-Stokes flow in a plane}

In this section, we review the derivation of the
modified Stokeslet, but for the imaginary parameter
regime --- which we will call the Helmholtz Stokeslet ---
which is the appropriate setting for the Stokes
eigenvalue problem.
The original modified Stokeslet is more well known,
and is of particular interest for its application to
numerical simulations of the unsteady Stokes equations
\cite{pozrikidis1992boundary,biros2002embedded}.

To begin, we restate the Stokes eigenvalue
problem as
\begin{align}
  \nabla p - \Delta \uu - k^2 \uu &= 0 \; , \label{eq:helmstokes}\\
  \nabla \cdot \uu &= 0 \; . \label{eq:helmstokescty}
\end{align}
Consider the solution of this problem where a
$\delta$ centered at $\yy$ with strength $\ff$
has been added to the right-hand side, i.e.

\begin{align}
  \nabla p - \Delta \uu - k^2 \uu &= \delta_\yy \ff \; ,
  \label{eq:helmstokes_charge} \\
  \nabla \cdot \uu &= 0 \; .
\end{align}
Note that

\begin{equation}
  \Delta G_L(\xx,\yy) = \delta_\yy(\xx) \; .
\end{equation}
If we substitute this expression into
\eqref{eq:helmstokes_charge} and take the divergence,
we obtain

\begin{equation}
  p = \nabla G_L(\xx,\yy) \cdot \ff \; .
\end{equation}
We then have, formally,

\begin{align}
  \uu &= - (\Delta + k^2)^{-1} ( \Delta G_L \ff
  - \nabla (\nabla G_L \cdot \ff ) ) \\
  &= \left ( -\Delta + \nabla \otimes \nabla \right )
  G_{BH} \ff \; .
\end{align}
The tensor

\begin{equation}
  \GG = - \II \Delta G_{BH} + \nabla \otimes \nabla G_{BH}
\end{equation}
is then the equivalent of a Stokeslet
\cite{pozrikidis1992boundary} for the problem
\eqref{eq:helmstokes}.

@@

\begin{align}
  T_{ijk} &= - \partial_{x_j} G_L \delta_{ik}
  + \partial_{x_k} \left ( -\Delta G_{BH} \delta_{ij} +
  \partial_{x_i} \left(\partial_{x_j} G_{BH} \right) \right)
  \nonumber \\
  & \qquad+ \partial_{x_i} \left ( -\Delta G_{BH} \delta_{kj} +
  \partial_{x_k} \left(\partial_{x_j} G_{BH} \right) \right)
  \; .
\end{align}
Let $u_i = G_{ij} f_j$ and $p = \partial_{x_i} G_L f_i$ be a
solution of the Stokes equations induced by a Stokeslet.
Then the corresponding stress tensor is given by
$\sigma_{ik} = T_{ijk} f_j$.

@@

\begin{equation}
  \TT_{\cdot,\cdot,k} \nu_k = -\bnu \otimes \nabla G_L
  + \partial_\nu \left ( -\Delta G_{BH} \II
  + \nabla \otimes \nabla G_{BH} \right)
  + \nabla \otimes \left ( -\Delta G_{BH} \bnu
  + \partial_{\nu} \nabla G_{BH} \right) \; .
\end{equation}
%\begin{align}
% -\Delta G_{BH} \bnu
% + \partial_{\nu} \nabla G_{BH} &=
% ( (-\partial_{x_1x_1}-\partial_{x_2x_2}) \nu_1 G_{BH} +
% (\partial_{x_1x_1}\nu_1 + \partial_{x_2x_1} \nu_2 )G_{BH},
% (-\partial_{x_1x_1}-\partial_{x_2x_2}) \nu_2 G_{BH} +
% (\partial_{x_1x_2}\nu_1 + \partial_{x_2x_2} \nu_2 )G_{BH}) \\
% &= (-\partial_{x_2} \partial_\tau G_{BH},
% \partial_{x_1} \partial_\tau G_{BH})
%\end{align}
%\begin{equation}
%  \begin{pmatrix}
%    -\partial_{x_2x_2} & \partial_{x_1x_2} \\
%    \partial_{x_1x_2} & -\partial_{x_1x_1}
%  \end{pmatrix} = -\nabla^\bot \otimes \nabla^\bot
%\end{equation}
Let $\btau = \bnu^\bot$. Then

\begin{equation}
  \TT_{\cdot,\cdot,k} \nu_k = -\bnu \otimes \nabla G_L
  - \nabla^\bot \otimes \nabla^\bot \partial_\nu G_{BH}
  +\nabla \otimes \nabla^\bot \partial_\tau G_{BH} \; .
\end{equation}

\subsection{Layer potentials}

@@

\begin{align}
  \left ( \TT_{\cdot,\cdot,k}\nu_k(\yy) \right )^\intercal
  \bmu(\yy) &= \left ( - \nabla G_L(\xx,\yy) + 2 \nabla^\bot
  \partial_{\nu\tau} G_{BH}(\xx,\yy) \right ) \mu_\nu(\yy) \nonumber \\
  & \qquad+
  \nabla^\bot \left (\partial_{\tau\tau}-\partial_{\nu\nu} \right )
  G_{BH}(\xx,\yy) \mu_\tau(\yy) \; .
\end{align}

\subsection{The Farkas integral representation}

As mentioned in the introduction, there are existing 
integral representations for the solution of the Dirichlet problem for the Helmholtz-biharmonic equation
\begin{align}
 \Delta (\Delta + k^2) w &= 0 \mbox{ in } D \; , \label{eq:biharmD1}\\
 w &= f \mbox{ on }
 \Gamma \label{eq:biharmD2} \; , \\ 
 \frac{\partial w}{\partial n} &= g \mbox{ on } 
 \Gamma \, , \label{eq:biharmD3}
\end{align}
In \cite{Farkas89}, 
the solution is given as the sum of two layer potentials, i.e.
where $\sigma_1$ and $\sigma_2$ are unknown densities.

The integral kernels, $K_1^F$ and $K_2^F$ are based on
derivatives of the Green's function for the biharmonic equation.

>>>>

\subsection{Green's functions}

Let $L_x$ denote a linear differential operator. A fundamental
solution $G(\xx,\yy)$ of $L_x$ satisfies the equation
$L_x G(\xx,\yy) = \delta_y(\xx)$ in the distributional sense, i.e.
for sufficiently smooth $f$
\begin{equation}
  L_x \int_{\R^2} G(\xx,\yy) f(\yy) \, dy = f(\xx) \; .
\end{equation}
We consider here
``free-space'' Green's functions, i.e. fundamental solutions which satisfy
some natural growth or decay conditions as $|\xx-\yy| \to \infty$.
The Green's function of the Helmholtz-biharmonic equation
\cref{eq:buck1} is given by 
\begin{equation}
  \Gbh(\xx,\yy) = -\frac{1}{k^2}
  \left (\frac{1}{2\pi} \log |\xx-\yy| +
  \frac{i}{4} H_0^{(1)}(k|\xx-\yy|) \right ) \, , 
\end{equation}
where $k$ is the Helmholtz paramater in the Helmholtz-Biharmonic equation,
and $H_{0}^{1}(r)$ is the Hankel function of the first kind of order zero.
Note that this is a scaled difference of the Green's function for
Laplace, i.e.

\begin{equation}
  \Glap(\xx,\yy) = -\frac{1}{2\pi} \log |\xx-\yy| \; ,
\end{equation}
and the Green's function for the Helmholtz equation

\begin{equation}
  \Ghelm(\xx,\yy) = \frac{i}{4} H_0^{(1)}(k|\xx-\yy|) \; .
\end{equation}

@@

In \cite{Farkas89}, Farkas derived integral equation formulations
for the solution of the Dirichlet problem for the biharmonic equation ($k=0$). 
In this formulation, the solution 
$w$ is represented as a sum of two layer potentials
\begin{equation}
  w(\xx) = \int_\Gamma \Kfark_1 (\xx,\yy) \sigma_1(\yy) \, dS(\yy)
  + \int_\Gamma \Kfark_2(\xx,\yy) \sigma_2(\yy) \, dS(\yy) \; ,
  \label{eq:farkRep}
\end{equation}
where $\sigma_{1}$, and $\sigma_{2}$ are unknown densities, and the kernels
$K_{1}^{F}$, and $K_{2}^{F}$ are linear combinations of derivatives of
the biharmonic Green's function and appropriately chosen to get second kind integral equations
for the unknown densities $\sigma_{1}$ and $\sigma_{2}$ on imposing the boundary conditions.

In \cite{jiang2013second}, Jiang extended the Farkas formulation for the solution of the modified
biharmonic equation, albeit for different boundary conditions. With minor modifications, their formulation
can also be adopted for the solution of the Dirichlet problem for the Helmholtz-biharmonic equation
\begin{align}
\Delta (\Delta + k^2) w &= 0 \quad \text{in} \quad \Omega \label{eq:helmbi} \\
w &= f \quad \text{on} \quad \Gamma \\
\dwdn &=g \quad \text{on} \quad \Gamma \,,
\end{align}
where $f,g$ are prescribed functions on the boundary.

For two points on the plane, $\xx$ and $\yy$, let $\br = \yy - \xx$. Let the kernels $K_{1}^{F}$, and 
$K_{2}^{F}$ be defined by 
\begin{align}
  \Kfark_1(\xx,\yy) &= \partial_{n_{y}n_{y}n_{y}}\Gbh(\xx,\yy)
  + 3 \partial_{n_{y}\tau_{y}\tau_{y}}\Gbh(\xx,\yy) + k^{2} \partial_{n_{y}}\Gbh(\xx,\yy)\; , \label{eq:kf1} \\
  \Kfark_2(\xx,\yy) &= -\partial_{n_{y}n_{y}}\Gbh(\xx,\yy)
  + \partial_{\tau_{y}\tau_{y}}\Gbh(\xx,\yy) \label{eq:kf2} \; .
\end{align}
More explicitly, we have
\begin{align}
  \Kfark_1(\xx,\yy) &=  -\dfrac{\br \cdot \bn(\yy)}{|\br|^2}  \cdot \left( \frac{3 i}{2} H_0^{(1)}(k|\br|) - \frac{5 i}{2 k|\br|} H_1^{(1)}(k|\br|) + \frac{6}{\pi k^2 |\br|^2} + \frac{1}{2\pi}  \right) +     \\
  & \quad \dfrac{\left(\br \cdot \bn(\yy)\right)^3}{|\br|^4} \cdot \left( 2i H_0^{(1)}(k|\br|) - \frac{7 i}{2 k|\br|} H_1^{(1)}(k|\br|) + \frac{8}{\pi k^2 |\br|^2}  \right) \, , \nonumber \\
  \Kfark_2(\xx,\yy) &=  -\left(\frac{1}{2}-\dfrac{\left(\br \cdot \bn(\yy)\right)^2}{|\br|^2} \right)  \cdot \left( \frac{i}{2} H_0^{(1)}(k|\br|) - \frac{i}{k|\br|} H_1^{(1)}(k|\br|) + \frac{2}{\pi k^2 |\br|^2}  \right)\; .
\end{align}

On enforcing the Dirichlet boundary conditions for
$w$, we obtain the integral equation
\begin{equation}
  \begin{split}
    \begin{pmatrix}
      f(\xx) \\
      g(\xx)
    \end{pmatrix} &= 
    \int_\Gamma
    \begin{pmatrix}
      \Kfark_{11}(\xx,\yy) & \Kfark_{12}(\xx,\yy) \\
      \Kfark_{21}(\xx,\yy) & \Kfark_{22}(\xx,\yy)
    \end{pmatrix}
    \begin{pmatrix}
      \sigma_1(\yy)\\
      \sigma_2(\yy)
    \end{pmatrix}
    \, dS(\yy) \\
    &\quad + \begin{pmatrix}
      1/2 & 0 \\
      -\kappa(\xx) & 1/2
    \end{pmatrix}
    \begin{pmatrix}
      \sigma_1(\xx)\\
      \sigma_2(\xx)
    \end{pmatrix} \; , \label{eq:farkIntEq} 
  \end{split}
\end{equation}
where $\kappa$ is the signed curvature at $\xx \in \Gamma$.
The kernels are given
by $\Kfark_{11} = \Kfark_1$, $\Kfark_{12} = \Kfark_2$,
\begin{align}
  \Kfark_{21}(\xx,\yy) &= \left(\Kfark_1(\xx,\yy)\right )_{n_x} \nonumber \\
  &= \bn(\xx) \cdot \nabla_{\xx} K_{21}^{F}(\xx,\yy) \; \label{eq:farkK21},\\
  \Kfark_{22}(\xx,\yy) &= \left(\Kfark_2(\xx,\yy)\right )_{n_x} \nonumber \\
  &= \bn(\xx) \cdot \nabla_{\xx} K_{22}^{F}(\xx,\yy) \label{eq:farkK22} \; .
\end{align}

@@

\begin{proof}
  The proof is a minor modification of the one presented in~\ref{eq:shidongmodbi}
  and is contained in~\cref{sec:farkproof}.
\end{proof}

The kernels $\Kfark_1$ and $\Kfark_2$ are
constructed with the goal that the $\Kfark_{ij}$ are
as smooth as possible. Suppose that the boundary
$\Gamma$ is of class $C^k$. Then, the kernels,
$\Kfark_{ij}(\xx,\yy)$, are $C^{k-2}$ functions on the boundary
for each $\yy \in \Gamma$.
Therefore, on a smooth
boundary, these kernels are smooth. However, on a
domain with a corner, we note 
that the kernel $\Kfark_{21}$
has a singularity with strength $r^{-2}$ (see~\cref{fig:ker21plot}). 
This singularity, in addition to the term in \cref{eq:farkIntEq}
which explicitly involves the
curvature, makes the representation \cref{eq:farkRep}
unstable for domains with high curvature (or
corners).

\subsection{An integral representation for the Stokes eigenvalue
  problem}

The Stokes eigenvalue problem (with ``no-slip'' boundary conditions)
seeks values $k^2$ such that the equations
\begin{align}
  \nabla p - \Delta \uu - k^2 \uu &= 0 \quad \textrm{in} \quad \Omega
  \; , \label{eq:helmstokes}\\
  \nabla \cdot \uu &= 0 \quad \textrm{in} \quad \Omega
  \; , \label{eq:helmstokescty} \\
  \uu &= 0 \quad \textrm{on} \quad \Gamma \; \label{eq:helmstokesnoslip}
\end{align}
have a non-trivial solution. In the case that $k=i\alpha$ for
some real-valued $\alpha$, the equations \cref{eq:helmstokes,eq:helmstokescty}
are known as the modified Stokes equations and are of particular
interest for their application to numerical simulations of unsteady
flow
\cite{pozrikidis1992boundary,biros2002embedded,jiang2013second}.
In the absence of a preferred name for the case of real-valued $k$,
we will refer to \cref{eq:helmstokes,eq:helmstokescty} as the
Helmholtz-Stokes equations.

\subsubsection{Stokeslets and stresslets}

In this section, we review the derivation of the
modified Stokeslet, but for the imaginary parameter
regime, which is the appropriate setting for the Stokes
eigenvalue problem.
The original modified Stokeslet is more well known,
and is of particular interest for its application to
numerical simulations of the unsteady Stokes equations
\cite{pozrikidis1992boundary,biros2002embedded}.

 Consider the solution of
\cref{eq:helmstokes,eq:helmstokescty} where a $\delta$-mass
centered at $\yy$ with strength $\ff$
has been added to the right-hand side of \cref{eq:helmstokes}, i.e.

\begin{align}
  \nabla p - \Delta \uu - k^2 \uu &= \delta_\yy \ff \; ,
  \label{eq:helmstokes_charge} \\
  \nabla \cdot \uu &= 0 \; .
\end{align}
Recall that

\begin{equation}
  \Delta \Glap(\xx,\yy) = \delta_\yy(\xx) \; .
\end{equation}
If we substitute this expression into
\eqref{eq:helmstokes_charge} and take the divergence,
we obtain

\begin{equation}
  p = \nabla \Glap(\xx,\yy) \cdot \ff \; .
\end{equation}
We then have, formally,

\begin{align}
  \uu &= - (\Delta + k^2)^{-1} ( \Delta \Glap \ff
  - \nabla (\nabla \Glap \cdot \ff ) ) \\
  &= \left ( -\Delta + \nabla \otimes \nabla \right )
  \Gbh \ff \; .
\end{align}
The tensor

\begin{equation}
  \GG = - \II \Delta \Gbh + \nabla \otimes \nabla \Gbh
\end{equation}
is then the equivalent of a Stokeslet
\cite{pozrikidis1992boundary} for the problem
\eqref{eq:helmstokes}.

@@

\begin{align}
  T_{ijk} &= - \partial_{x_j} \Glap \delta_{ik}
  + \partial_{x_k} \left ( -\Delta \Gbh \delta_{ij} +
  \partial_{x_i} \left(\partial_{x_j} \Gbh \right) \right)
  \nonumber \\
  & \qquad+ \partial_{x_i} \left ( -\Delta \Gbh \delta_{kj} +
  \partial_{x_k} \left(\partial_{x_j} \Gbh \right) \right)
  \; .
\end{align}
Let $u_i = G_{ij} f_j$ and $p = \partial_{x_i} \Glap f_i$ be a
solution of the Stokes equations induced by a Stokeslet.
Then the corresponding stress tensor is given by
$\sigma_{ik} = T_{ijk} f_j$.

@@

\begin{equation}
  \TT_{\cdot,\cdot,k} \nu_k = -\bnu \otimes \nabla \Glap
  + \partial_\nu \left ( -\Delta \Gbh \II
  + \nabla \otimes \nabla \Gbh \right)
  + \nabla \otimes \left ( -\Delta \Gbh \bnu
  + \partial_{\nu} \nabla \Gbh \right) \; .
\end{equation}
%\begin{align}
% -\Delta \Gbh \bnu
% + \partial_{\nu} \nabla \Gbh &=
% ( (-\partial_{x_1x_1}-\partial_{x_2x_2}) \nu_1 \Gbh +
% (\partial_{x_1x_1}\nu_1 + \partial_{x_2x_1} \nu_2 )\Gbh,
% (-\partial_{x_1x_1}-\partial_{x_2x_2}) \nu_2 \Gbh +
% (\partial_{x_1x_2}\nu_1 + \partial_{x_2x_2} \nu_2 )\Gbh) \\
% &= (-\partial_{x_2} \partial_\tau \Gbh,
% \partial_{x_1} \partial_\tau \Gbh)
%\end{align}
%\begin{equation}
%  \begin{pmatrix}
%    -\partial_{x_2x_2} & \partial_{x_1x_2} \\
%    \partial_{x_1x_2} & -\partial_{x_1x_1}
%  \end{pmatrix} = -\nabla^\bot \otimes \nabla^\bot
%\end{equation}
Let $\btau = \bnu^\bot$. Then

\begin{equation}
  \TT_{\cdot,\cdot,k} \nu_k = -\bnu \otimes \nabla \Glap
  - \nabla^\bot \otimes \nabla^\bot \partial_\nu \Gbh
  +\nabla \otimes \nabla^\bot \partial_\tau \Gbh \; .
\end{equation}

\subsubsection{Layer potentials and integral representation}

@@

\begin{align}
  \left ( \TT_{\cdot,\cdot,k}\nu_k(\yy) \right )^\intercal
  \bmu(\yy) &= \left ( - \nabla \Glap(\xx,\yy) + 2 \nabla^\bot
  \partial_{\nu\tau} \Gbh(\xx,\yy) \right ) \mu_\nu(\yy) \nonumber \\
  & \qquad+
  \nabla^\bot \left (\partial_{\tau\tau}-\partial_{\nu\nu} \right )
  \Gbh(\xx,\yy) \mu_\tau(\yy) \; .
\end{align}
